### 2017-01-20 paper/intro.tex
pass on section 2

At large organizations, the alternative of renting cloud
services\footnote{List of popular cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware, perhaps existing hardware, emerges as an attractive solution
for running tests.  The proliferation of multi-core CPUs and the
increasing popularization of testing frameworks with a rich support
for parallelization enables test suite speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  This paper reports on an
empirical study we conducted to analyze importance of low-level
parallelization to speedup testing of open-source projects.  This is a
relevant problem given the tremendous popularity of open-source
development and regression testing research.

@@

\begin{itemize}
\item \textbf{Prevalence of long-running test suites.}
\item \textbf{Usage of test suite parallelization.}  
\item \textbf{Impact of parallelization.}
\item \textbf{Issues with parallelization.}    
\end{itemize}

@@

%%RQ3
Given the high execution cost associated with a significant number of
\github{} projects, we decided to investigate practical usage of test
suite parallelization.  It is important to note that modern build
systems (\eg{}, Maven~\cite{maven}) offer parallelization options to
accelerate test execution (see Section~\ref{sec:modes}).  To find how
popular are these features in practice, we first analyzed build files
\emph{statically}.  Considering the +1m group of projects
(\numMedLong{} in total), we found that 49\% (41/\numMedLong{}) of
them use some parallelization option.  Considering those projects that
take more than 5m to run (\numLong{} in total), usage of parallelism
increases to 59\% (19/\numLong{}).  Furthermore, we found that
``forking'' virtual machines was the most prevalent parallel mode used
in practice.  It appeared twice as much as any other mode.  This
result suggests that datarace flakiness~\cite{luo-etal-fse2014} may be
a concern to users as ``forking'' creates different independent
processes (\ie{}, Java VM instances) to speedup test execution.  It
does not exploit thread-level concurrency within each VM, which can be
an important source of
contention~\cite{bell-kaiser-icse2014,bell-etal-esecfse2015}.
\Mar{why 32-19 did not use parallelization?} \Mar{what about free
  services (jenkins)?  how much can you scale execution and how
  expensive would that be?}

>>>>

At large organizations, the alternative of renting cloud
services\footnote{List of popular cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware, perhaps existing hardware, emerges as an attractive solution
for running tests.  The proliferation of multi-core CPUs and the
increasing popularization of testing frameworks with a rich support
for parallelization enables test suite speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  This paper reports on an
empirical study we conducted to analyze the impact of low-level
parallelization to speedup testing in open-source projects.  This is a
relevant problem given the tremendous popularity of open-source
development and regression testing research.

@@

\begin{itemize}
\item \textbf{Prevalence of long-running test suites.}
\item \textbf{Usage of test suite parallelization.}  
\item \textbf{Speedups of parallelization modes.}
\item \textbf{Issues with parallelization.}    
\end{itemize}

@@

%%RQ3
Given the high execution cost associated with a significant number of
\github{} projects, we decided to investigate practical usage of test
suite parallelization.  It is important to note that modern build
systems (\eg{}, Maven~\cite{maven}) offer parallelization options to
accelerate test execution (see Section~\ref{sec:modes}).  To find how
popular are these features in practice, we first analyzed build files
\emph{statically}.  Considering the +1m group of projects
(\numMedLong{} in total), we found that 49\% (41/\numMedLong{}) of
them use some parallelization option.  Considering those projects that
take more than 5m to run (\numLong{} in total), usage of parallelism
increases to 59\% (19/\numLong{}).  Furthermore, we found that
``forking'' virtual machines was the most prevalent parallel mode used
in practice.  This mode is used twice as much as any other mode used.
Important to note that ``forking VMs'' is perhaps the simplest of the
parallelization modes~--~it is provided by the build system as opposed
to the testing framework.  This result suggests that datarace
flakiness~\cite{luo-etal-fse2014} may be a concern to users as
``forking'' does not exploit thread-level concurrency within each VM,
which can create contention on data reachable from the static
area~\cite{bell-kaiser-icse2014,bell-etal-esecfse2015}.  Instead, it
creates independent processes (\ie{}, Java VM instances) and executes
tests sequentially within each process. \Mar{why 32-19 did not use
  parallelization?} \Mar{what about free services (jenkins)?  how much
  can you scale execution and how expensive would that be?}

### 2017-01-20 paper/modes.tex
pass on section 2

Parallelism in test execution can be obtained at different levels.
Figure~\ref{fig:levels} illustrates relevant levels for this paper.
The highest level indicates parallelism that can be obtained through
different machines on the network.  For examples, using machines from
a cloud service.  The machine space sits under the ``network space'',
and is responsible to provide low-level parallelism.  In that case,
computation can be offloaded on different CPUs within a machine and on
different threads within each CPU.  Note that all these levels are
complementary.  For the scenario of large IT organizations, for
example, lower-level parallelization schemes could leverage the
computing power of server nodes in addition to the aggregate
processing power of the farm.

@@

This paper focuses at lower-level parallelism, which can be enabled
through build systems and testing frameworks.  Given the proliferation
of multi-core machines it is not surprising that testing frameworks
provide today support for parallel test
execution~\cite{junit-org,testng,nunit}.  Build systems wrap parallel
features offered by testing frameworks to facilitate the use of such
technology~\cite{maven-surefire-plugin}.  In the following we elaborate
relevant features of these components focusing on Java, Maven, and
JUnit but the discussion can be generalized to other languages, build
systems, and testing frameworks.

@@

\Mar{----------------------- estou aqui.}

\subsection{Testing Framework}
\label{sec:frameworks}

@@

\begin{itemize}
\item
    \textbf{Sequential (\Seq).}~This configuration results in
        sequential execution of test classes and their methods,
        according to a given order defined in the testing framework
        (\eg, the order of methods returned by Java Reflection
        API)~\cite{junit-test-order}. For JUnit, this is the default
        configuration.
\item
    \textbf{Sequential classes; parallel methods
        (\ParClassSeqMeth{}).}~This configuration results in the
        sequential execution of the test classes assigned to the JVM.
        However, within each class, test methods run in parallel. In
        JUnit, \emph{ParallelComputer} provides support to parallel
        execution: it instantiates a test runner with an
        \emph{ExecutorService} from the Java Concurrent API. Each test
        method is executed in a separated thread as the thread pool
        creates new threads on-demand and reuse them if any thread is
        available.
    \Comment{http://junit.org/junit4/javadoc/latest/src-html/org/junit/experimental/ParallelComputer.html#line.14}
\item
    \textbf{Parallel classes; sequential methods
        (\SeqClassParMeth{}).}~This configuration results in the
        parallel execution of test classes and sequential test
        methods. As in \ParClassSeqMeth, the test runner has a cached
        thread poll but instead of executing test methods from a
        single test class, the test suite runner executes classes in
        separated threads and methods sequentially within each thread.
\item
    \textbf{Parallel methods (\ParClassParMeth).}~This configuration
        results in the parallel execution of any test method from any
        class.  \Jbc{I need to confirm this but AFAIK this is how it
        happens} As in \SeqClassParMeth, classes execute on separated
        threads but test methods are also executed in parallel. More
        precisely, there is a thread pool to execute classes in
        separated threads (\ie, like in \ParClassSeqMeth) and, within
        each class runner, there is an \emph{ExecutorService} to run
        test methods in parallel (\ie, like in \SeqClassParMeth).
\end{itemize}

@@

\subsection{Build Systems}
Build systems, such as Maven\footnote{\url{maven.apache.org}},
typically provide the option to \emph{fork} JVM instances
proportionally to available cores in the machine.  If the option
``fork JVM'' is enabled, Maven will allocate a user-provided number of
JVM instances to each core in the machine and will allocate each test
class to exactly one JVM.  Note that there is no guarantee to
uniformly distribute load to each JVM given that the build system uses
classes as the unit to specify test tasks.\Fix{we need to know how
Maven allocates test classes to JVMs}

>>>>

Parallelism in test execution can be obtained at different levels.
Figure~\ref{fig:levels} illustrates relevant levels.  The highest
level indicates parallelism that can be obtained through different
machines on the network.  For examples, using virtual machines from a
cloud service.  The machine space sits under the ``network space'' and
provides \emph{low-level parallelism}.  In that case, computation can
be offloaded at different CPUs within a machine and at different
threads within each CPU.  Note that all these levels are
complementary.  For example, lower-level parallelization schemes could
leverage the computing power of server nodes in addition to the
aggregate processing power of the farm.

@@

This paper focuses at lower-level parallelism, which can be enabled 
through build systems and testing frameworks.  Given the proliferation
of multi-core machines it is not surprising that testing frameworks
provide today support for parallel test execution (e.g.,
JUnit~\cite{junit-org}, TestNG~\cite{testng}, and NUnit~\cite{nunit}).
Build systems wrap parallel features offered by testing frameworks to
facilitate the use of such technology~\cite{maven-surefire-plugin}.
In the following we elaborate relevant features of these components
focusing on Java, Maven, and JUnit but the discussion can be
generalized to other languages, build systems, and testing frameworks.

@@

\subsection{Testing Frameworks}
\label{sec:frameworks}

@@

\begin{itemize}
\item
    \textbf{Sequential (\Seq).}~This configuration corresponds to the
    sequential execution of test classes and, for each class,
    sequential execution of their methods.  The execution order (of
    classes and methods) is determined by the testing framework (\eg,
    the order of methods returned by the Java Reflection
    API)~\cite{junit-test-order}.
\item
    \textbf{Sequential classes; parallel methods
      (\ParClassSeqMeth{}).}~This configuration corresponds to the
    sequential execution of the test classes assigned to the JVM.
    However, within each class, test methods run in parallel.
\item
    \textbf{Parallel classes; sequential methods
      (\SeqClassParMeth{}).}~This configuration corresponds to the
    parallel execution of test classes with sequential execution of
    their test methods.
\item
    \textbf{Parallel methods (\ParClassParMeth).}~This configuration
    corresponds to the parallel execution of any test method from any
    class.
\end{itemize}

\Seq{} is the default configuration.  In constrast to the other modes,
it does not use parallelism.  Considering use of parallelism,
\ParClassParMeth{} is the most agressive mode, with \ParClassSeqMeth{}
and \SeqClassParMeth{} lying between \Seq{} and \ParClassParMeth{}.
\ParClassSeqMeth{} and \SeqClassParMeth{} run sequentially either
classes or methods.  Intuititvely, fixing one of these dimensions
enables developers to better organize their test suites as to avoid
dataraces~\Fix{cite}.  JUnit implements these modes through a set of
customized classes (e.g., \CodeIn{ParalllelComputer} and
\CodeIn{ExecutorService}).

%% \Fix{-----}
%% In JUnit, \emph{ParallelComputer} provides support to parallel
%% execution: it instantiates a test runner with an
%% \emph{ExecutorService} from the Java Concurrent API. Each test method
%% is executed in a separated thread as the thread pool creates new
%% threads on-demand and reuse them if any thread is available.
%% \Comment{http://junit.org/junit4/javadoc/latest/src-html/org/junit/experimental/ParallelComputer.html#line.14}

%% As in \ParClassSeqMeth, the test runner has a cached thread poll but
%% instead of executing test methods from a single test class, the test
%% suite runner executes classes in separated threads and methods
%% sequentially within each thread.

%% \Jbc{I need to confirm this but AFAIK this is how it happens} As in
%% \SeqClassParMeth, classes execute on separated threads but test
%% methods are also executed in parallel. More precisely, there is a
%% thread pool to execute classes in separated threads (\ie, like in
%% \ParClassSeqMeth) and, within each class runner, there is an
%% \emph{ExecutorService} to run test methods in parallel (\ie, like in
%% \SeqClassParMeth).

%% \Fix{-----}

\subsection{Build Systems}

\Fix{--------------------- estou aqui}

@@

Build systems, such as Maven\footnote{\url{maven.apache.org}},
typically provide the option to \emph{fork} JVM instances
proportionally to available cores in the machine.  If the option
``fork JVM'' is enabled, Maven will allocate a user-provided number of
JVM instances to each core in the machine and will allocate each test
class to exactly one JVM.  Note that there is no guarantee to
uniformly distribute load to each JVM given that the build system uses
classes as the unit to specify test tasks.\Fix{we need to know how
Maven allocates test classes to JVMs}
